Query Optimization for Dynamic Imputation

### 2017-05-02 paper/experiments.tex
prettify missing values tables

\begin{table}
  \centering
  \begin{subtable}{0.5\textwidth}
    \centering
    \input{tables/cdc_demo}
    \caption{Demographics (\texttt{demo}). \demorows{} rows.}
  \end{subtable}
  \par\medskip
  \begin{subtable}{0.5\textwidth}
    \centering
    \input{tables/cdc_labs}
    \caption{Laboratory Results (\texttt{labs}). \labexrows{} rows.}
  \end{subtable}
  \par\medskip  
  \begin{subtable}{0.5\textwidth}
    \centering
    \input{tables/cdc_exams}
    \caption{Physical Results (\texttt{exams}). \labexrows{} rows.}
  \end{subtable}
  \par\medskip  
  \caption{Missing value distribution for each table/attribute in CDC NHANES 2013--2014 data.}\label{table:nhanes-description} 
\end{table}

@@

\begin{table}
  \centering
  \input{tables/fcc}
  \caption{Missing value distribution for each attribute in freeCodeCamp Survey Data (\texttt{fcc})}\label{table:fcc-description} 
\end{table}

@@

\Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error
(SMAPE)~\cite{Makridakis2000451} for \ProjectName{}'s query results when compared to
imputing on the base tables and executing the query on this cleaned base data.
This measure indicates how much error is introduced by on-the-fly imputation compared to
imputation on the base tables. This comparison is the relevant one in practice --- an
analyst would only be considering the trade-offs in imputation quality and time in the first
place for dirty input data, for which ground truth is unavailable.

In our case, the relevant comparison is against traditional
imputation on the base table, given the unavailability of ground truth.

>>>>

\begin{table*}
  \centering
  \begin{subtable}{0.3\textwidth}
    \centering
    \input{tables/cdc_demo}
    \caption{Demographics (\texttt{demo}). \demorows{} rows.}
  \end{subtable}\quad\begin{subtable}{0.3\textwidth}
    \centering
    \input{tables/cdc_labs}
    \caption{Laboratory Results (\texttt{labs}). \labexrows{} rows.}
  \end{subtable}\quad\begin{subtable}{0.3\textwidth}
    \centering
    \input{tables/cdc_exams}
    \caption{Physical Results (\texttt{exams}). \labexrows{} rows.}
  \end{subtable}
  \caption{Percentage of values missing in the CDC NHANES 2013--2014 data.}\label{table:nhanes-description} 
\end{table*}

@@

\begin{table}
  \centering
  \input{tables/fcc}
  \caption{Percentage of values missing in the freeCodeCamp Survey data (\texttt{fcc}).}\label{table:fcc-description} 
\end{table}

@@

\Cref{table:smape} shows the Symmetric-Mean-Absolute-Percentage-Error
(SMAPE)~\cite{Makridakis2000451} for \ProjectName{}'s query results when compared to
imputing on the base tables and executing the query on this cleaned base data.
This measure indicates how much error is introduced by on-the-fly imputation compared to
imputation on the base tables. In our case, the relevant comparison is against traditional
imputation on the base table, given the unavailability of ground truth.
